\emph{Alles hat ein Ende, aber ein Wurst hat zwei.}
\\
First and foremost thanks to my supervisors, Elias Metral and Roger Jones. You've provided, in your own ways, insight and guidance that helped get this work on the road and ultimately to it's destination. Particular thanks to Elias for being willing to answer my questions, no matter how basic, convoluted, badly explained or even entirely relevant they may be. An additional thanks should go to my "not-supervisor" supervisors Mike Barnes and Fritz Caspers. Mike for your constant interest in my work and taking the time to explain the more technical aspects of magnet operations. And Fritz, CERN's persistent bastion of wisdom. Your tenacity, even if... especially if delivered with your usual flair is always refreshing, even if it requires twice the work to satisfy.
\\
To my friends at work, both near and far. I've bothered you with questions, queries and inane banter for 3 years and you still haven't lynched me! Nicolas, Niccolo, Carlo, Serena, Olav, Jean-Luc many thanks to all of you for your assistance. Thanks to Adina and James "Oh god that beard is immense" M. in Manchester for listening to the frequent rant I'd have. And to all the members in the MEW group, past and present, for an abundance of technical support and advice. Especially to Ian for being an immense Dude! Further thanks to Prof. Vitorrio Vacarro, Alexej Grudiev and Alexey Burov. Your collective wisdom on all things RF and impedance has pulled me out of more holes than I can count by this point. And one final thanks to the Commisar of the Impedance Team - Benoit Salvant. A little hint, consistent questioning and the occassional boot to the posterior have been much appreciated over the years.
\\
To my family, either by blood or by choice. The gamers (Southampton and CERN) for incessantly dragging me away from reality into a strange dark place far from here, filled with demons, heroes and cake. The library crew for unintentionally providing me an outlet during those long times of writing amongst the books. Piotr, Ruben, Steffen, Joni and a number of others for dragging me up into the mountains and ensuring we all got back down intact. Penny, Jan, Nic, Victor, Joe and Steffen for providing somewhere I'm happy to return home to. The Random Trip Club for providing sugar and insanity in relatively equal portions. LHCz collaboration for getting me started on helping to make films, and the Zurichians for helping continue the path. Sharman and Oscar - whether intentionally or not you've both provided the means and motive to jump onto the Adventure over the years. Hopefully it's been worth it. And to Eric - the hardest lesson was learning you just need the right tool for the job. And enough perseverence to learn how to use it. Continue being awesome you all.
\\
And finally, a thank you to something special. Sight, sound, touch, smell and taste. With you there there's no gap to fill. Rakkatakka \m/.
